---
title: "Quick start: pctax"
output: 
  prettydoc::html_pretty:
    keep_md: true
    toc: true
    toc_depth: 3
    theme: architect
vignette: >
  %\VignetteIndexEntry{pctax}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE, cache = TRUE,
    comment = "#>",
    dpi = 72
)
```

```{r setup,include=FALSE}
library(pctax)
library(pcutils)
```

# pctax

`pctax` provides a comprehensive suite of tools for analyzing omics data.

## Vignette

Please go to <https://bookdown.org/Asa12138/pctax_book/> for the full vignette.

## Install

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("Asa12138/pcutils", dependencies = T)

devtools::install_github("Asa12138/pctax", dependencies = T)
```

## Usage
It includes functionalities for α-diversity analysis, β-diversity analysis, differential analysis, community assembly, visualization of phylogenetic tree and functional enrichment analysis... 

Look at the test data:
```{r lib}
library(pctax)
library(pcutils)
data(otutab, package = "pcutils")
# help(otutab)

head(otutab)
head(metadata)
head(taxonomy)
```

## Citation
Please cite:

Chen Peng (2023). _pctax: Professional Comprehensive Omics Data Analysis_. R package, <https://github.com/Asa12138/pctax>.
